\begin{skill}{Action surge \\\phantom{a}\hfill Levels: 2}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	You can choose to perform a fourth action each round. Regardless the actions you chose, your heart rate increases by 25\% / 15\% of your max heart rate minus current heart rate. Can't be performed while in Zone 3.\\

	\hfill
	\begin{tabular}{rrr}
		Costs: & 2000 & 2000 \\
		Spd: & 12 & 14 \\
		Foc: & 12 & 14 \\
	\end{tabular}
\end{skill}

\begin{skill}{Adrenaline surge (Passive) \\\phantom{a}\hfill Levels: 3}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	The character ignores the first 1/2/3 levels of pain occurring in combat, during this combat. Level 6 pain no longer results in unconsciousness. Benefit vanishes after combat.\\

	\hfill
	\begin{tabular}{rrrr}
		Costs: & 500 & 750 & 1000 \\
		Physical Fortitude: & 2 & 6 & 10 \\
	\end{tabular}
\end{skill}

\begin{skill}{Bringing a gun to a knife fight}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Mali for weapon engagements <1m are changed to the respective <20m mali, if smaller.

	Requires level 8 in the respective weapon skill.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 1000 \\
	\end{tabular}
\end{skill}

\begin{skill}{Bringing a knife to a gunfight}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Upon performing a successful throwing check you may target anything within your throw range and perform a knife attack with advantage against that target. Regardless of the throw check, you throw the knife and have to recover it.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 400 \\
	\end{tabular}
\end{skill}

\begin{skill}{Cover and concealment}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	You take 2 actions to prepare your surroundings (if possible, e.g. no use in empty corridors or on a basketball court.). When crouched/lying, your opponents get an additional attack mali of -1/-2 on you until you move or attack, and you might become harder to spot.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 350 \\
		Camouflage \& hiding: & 5 \\
	\end{tabular}
\end{skill}

\begin{skill}{Fast acquisition}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Fast acquisition increases heart rate by 10. Once per turn you can roll a coordination check to convert an unaimed shot into an aimed shot for free, if you can aim in this situation (e.g. not during a sprint).\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 400 \\
		Spd: & 13 \\
		Foc: & 15 \\
	\end{tabular}
\end{skill}

\begin{skill}{Fast draw \\\phantom{a}\hfill Levels: 2}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Fast draw increases heart rate by 5.

	1. Passing a Crd check lets you draw a weapon in one action and switch weapons in two actions.

	2. Drawing weapon’s takes one action, switching weapons takes two actions.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 300 \\
	\end{tabular}
\end{skill}

\begin{skill}{Fast reload \\\phantom{a}\hfill Levels: 2}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Fast reload increases heart rate by 5.

	1. Passing a Crd check reduces reload time by one action for any man-portable weapon except (sniper) rifles.

	2. Reload time is reduced by one for any portable weapon except (sniper) rifles.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 600 \\
	\end{tabular}
\end{skill}

\begin{skill}{Fire corridor (Reaction)}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Takes 3 actions. You set up a fire corridor, a 30° wide cone in front of you. Whenever something enters or leaves the corridor, or enters/ leaves full cover in the corridor, you can perform an aimed shot as a reaction twice until your next turn. Counts as readied action.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 400 \\
	\end{tabular}
\end{skill}

\begin{skill}{Honing in on target \\\phantom{a}\hfill Levels: 3}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Takes one action. You dedicate your Focus to one target. While you have line of sight to the target (or the conditions of “spatial awareness” or “steady aim” apply) you get +1/+2/+3 on your attack rolls against the target and -2/-4/-6 against all other targets.\\

	\hfill
	\begin{tabular}{rrrr}
		Costs: & 200 & 300 & 400 \\
		Foc: & 10 & 12 & 14 \\
	\end{tabular}
\end{skill}

\begin{skill}{Hug dirt (Reaction)}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Needs to be announced at the beginning of every battle round. After the first attack on you, if you are not lying already, you drop to the ground (breaking any readied reactions and so forth). Until your next round enemy’s get a -2 on their attacks on you, in addition to other bonuses due to the change of stance (when at a corner or similar you will also be considered at least at half cover afterwards). Can be used when targeted by burst or automatic fire, for which all but the first and any critical rolls need to be rerolled. Increases heart rate by 5.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 500 \\
	\end{tabular}
\end{skill}

\begin{skill}{In the hands of a master everything is a weapon \\\phantom{a}\hfill Levels: 2}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Get a +1/+2 modifier on all weapon skills below 8/12 (however, weapon skill + this modifier must not exceed the threshold). 

	Requires one weapon skill at 13/17.\\

	\hfill
	\begin{tabular}{rrr}
		Costs: & 2300 & 3000 \\
	\end{tabular}
\end{skill}

\begin{skill}{Keen eyes - behaviour}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	On a successful tactics check you receive information about the behaviour of an enemy. This takes an action to perform and requires line of sight with the target.

	The amount and detail of information scales with the quality level of the check. This information includes, but is not limited to: whether alerted, which direction they are moving, whom they are targeting, when they would flee combat, whether they are coordinating with partners, etc.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 500 \\
		Tactics: & 4 \\
	\end{tabular}
\end{skill}

\begin{skill}{Keen eyes - loadout}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	On a successful Weapons check you receive information about the combat loadout of an enemy. The amount and detail of information scales with the quality level of the check. This takes an action to perform and requires line of sight with the target.

	The information gained is linked to the QL of the check.

	  QL1-2: Information for the main weapon or the main armour is gained.

	  QL3-4: Information for both the main weapon and main armour is gained.

	QL1 and QL2, and QL3 and QL4 differ in the amount of details. For every QL over 4 one additional item is revealed or details for a revealed item is obtained.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 500 \\
		Weapons: & 4 \\
	\end{tabular}
\end{skill}

\begin{skill}{Keen eyes - training}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	On a successful Tactics check you receive information about the training state (aka skills) of an enemy. This takes an action to perform and requires line of sight with the target and the target has to be in a combative state or preparing for combat. 

	The information gained is linked to the QL of the check. Per QL a new skill (player’s choice whether combat skill, medical skill or general skill) is revealed or the level of the skill is revealed.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 500 \\
		Tactics: & 4 \\
	\end{tabular}
\end{skill}

\begin{skill}{Last stand (Passive) \\\phantom{a}\hfill Levels: 2}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	After receiving lethal damage and while your heart rate is >100/>60 you become immobilised instead of unconscious. While your HR is above this threshold you may still perform 3 actions per round, although with disadvantage by default. None of these actions increase your HR by themselves. After your HR falls below the threshold you are following the common rules for dying. Can be combined with 'unfinished business'.\\

	\hfill
	\begin{tabular}{rrr}
		Costs: & 750 & 750 \\
		Res: & 13 & 15 \\
	\end{tabular}
\end{skill}

\begin{skill}{Master chef}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	You can use one action to cook a grenade for exactly 1 or 2 seconds.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 400 \\
	\end{tabular}
\end{skill}

\begin{skill}{Never shall I fail}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Once every 3 days: For one battle or one physically strenuous task you ignore pain, fright, strain, and the first 4 levels of encumbrance. Additionally you gain a +2 Bonus on End and Res, your physical proficiencies and a +1 Bonus on your weapon skills. Furthermore you gain advantage on one arbitrary check, while this effect lasts.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 1000 \\
		Res: & 15 \\
	\end{tabular}
\end{skill}

\begin{skill}{Riding the lightning (LMG)}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	After announcing this you can only perform the unaimed shot action in burst or automatic until your magazine is empty, with the target chosen randomly to be any creature in a 40° cone and <50m from you (distance modifiers apply). Your unaimed shots are modified by the quality of a Str check, performed after announcing this skill. While riding the lightning you gain one bonus action per BR.

	You do not gain or lose Heart rate during this time.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 600 \\
		LMGs: & 9 \\
		Str: & 12 \\
	\end{tabular}
\end{skill}

\begin{skill}{Riding the lightning (SAB)}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	After announcing this you can only perform the unaimed shot action in burst or automatic until your charge pack is empty, with the target chosen randomly to be any creature in a 40° cone and <50m from you (distance modifiers apply). Your unaimed shots are modified by the quality of a Foc, performed after announcing this skill. While riding the lightning you gain one bonus action per BR.

	You do not gain or lose Heart rate during this time.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 600 \\
		SABs: & 9 \\
		Foc: & 12 \\
	\end{tabular}
\end{skill}

\begin{skill}{Shock and awe \\\phantom{a}\hfill Levels: 2}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Upon a successful Cha check every friendly creature addressed by you can ready up to three actions or less. All your teammates’ readied actions then occur simultaneously with your actions in the next BR. During this, enemies get disadvantage on their reactions and readied actions and hit enemies receive +0/+1/+2… levels of fright for each individual hit they receive during that time (bursts, automatic and shotgun shots count as one). Takes 3 actions to prepare, can only be used once/twice per combat (even if multiple characters possess this skill).\\

	\hfill
	\begin{tabular}{rrr}
		Costs: & 500 & 500 \\
		Cha: & 10 & 12 \\
		Tactics: & 4 & 7 \\
	\end{tabular}
\end{skill}

\begin{skill}{Spatial awareness (Passive)}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	If you had partial vision on a target, you can ignore mali from further vision reduction (e.g. due to cover or smoke grenades) for one battle round, after they got into effect. For targets in full cover damage modifiers might apply.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 350 \\
		Int: & 12 \\
	\end{tabular}
\end{skill}

\begin{skill}{Spray and pray}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	You can attempt suppressive fire out of full cover with disadvantage on the attack roll.\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 250 \\
	\end{tabular}
\end{skill}

\begin{skill}{Stable shooting platform \\\phantom{a}\hfill Levels: 3}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	1. Aimed shots and unaimed shoots without penalty can be performed during a stride at quarter speed for: pistols in general and blasters, shotguns, slug throwers with AI aim assistance. Aimed shots can be performed while standing, after running, for SABs and sniper rifles.

	2. Aimed shots and unaimed shoots without penalty can be performed during a stride at half speed for: pistols in general and blasters, shotguns, slug throwers with AI aim assistance (or at half speed without AI aim assistance). Aimed shots can be performed while striding at quarter speed for SABs in general and sniper rifles with AI aim assistance.

	 3.Aimed shots and unaimed shoots without penalty can be performed at full stride speed for: pistols in general and blasters, shotguns, slug throwers with AI aim assistance (or at a stride without AI aim assistance). Aimed shots can be performed while striding at half speed for SABs in general and sniper rifles with AI aim assistance (or at quarter stride speed without AI assistance).\\

	\hfill
	\begin{tabular}{rrrr}
		Costs: & 1000 & 1000 & 1000 \\
		Crd: & 12 & 14 & 16 \\
		Foc: & 12 & 14 & 16 \\
	\end{tabular}
\end{skill}

\begin{skill}{Steady aim \\\phantom{a}\hfill Levels: 3}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Requires level 12 in the weapon used. Can be combined with stable shooting platform.

	1. After a successful aimed shot with a blaster, pistol, shotgun, slug thrower, or SABs you can perform a Crd check. Upon success the next aimed shot on the same target will only costs one action. For slugthrowers, shotguns, and LMGs you have to pass a strength check after each shot to get this benefit. Receiving damage, being stunned or blinded, performing any other action than an aimed shot before the next shot, or losing line of sight will negate this effect.

	2. You can switch targets to anything in the same distance category or lower after passing the Crd check. Restrictions from level 1 apply. Exception: if you receive damage you have to pass a Foc check with a mali of 25\% of the received damage (after armor damage reductions) to keep the bonus.

	3. You can lose line of sight with a target, without losing your target lock (e.g. going in and out of cover) for one BR. Receiving damage only requires you pass a focus check in order to keep the previous bonuses. For slugthrowers, shotgun, SABs you have to pass a strength check with advantage to keep the target acquisition.\\

	\hfill
	\begin{tabular}{rrrr}
		Costs: & 1500 & 1500 & 1500 \\
		Foc: & 13 & 15 & 17 \\
	\end{tabular}
\end{skill}

\begin{skill}{Suppressive fire \\\phantom{a}\hfill Levels: 2}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Needs a burst fire or automatic weapon. Perform an attack roll against a target with +2/+4. This only deals damage 2/4 and if the target has at most half cover. During suppressive fire your Ammunition usage doubles.

	Every BR, while being suppressed, your target has to perform a Mental Fortitude check, with a mali of -1 per successful attack roll. If the target fails they receive 3 levels of fright while you maintain suppressive fire.

	Suppressive fire takes 3 actions to perform. Your target stays suppressed until your next turn.\\

	\hfill
	\begin{tabular}{rrr}
		Costs: & 300 & 500 \\
	\end{tabular}
\end{skill}

\begin{skill}{Tennis arm (Reaction) \\\phantom{a}\hfill Levels: 2}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Once per BR you can kick away a grenade landing without an action cost. Its direction is determined by an 1d8 (1 north, 3 east, 5 south…) a cooked grenade then explodes in 6m distance and an uncooked after 12m + 2m per QL in a Spd check.

	At level 2 you can also toss the grenade 2m per QL in a throw check in a direction of your choice or cover it in a det cover or an improvised object. This counts as one action at strain level 2 in your next turn, and breaks readied actions.\\

	\hfill
	\begin{tabular}{rrr}
		Costs: & 300 & 600 \\
		Spd: & 12 & 14 \\
		Foc: & 12 & 14 \\
		Throwing: &  & 5 \\
	\end{tabular}
\end{skill}

\begin{skill}{Unfinished business (Passive)}
	\setlength{\parskip}{8pt}
	\setlength{\parindent}{0pt}
	Once between long rests or receiving extensive medical attention: If you receive lethal damage, but not more than twice your max LP, you get two immediate actions and the lethal damage cannot bring your heart rate below 50. The two actions do not increase your heart rate. You get advantage on any roll during these two actions. After these actions you commence the dying process. Can be combined with 'last stand' (you are mobile during the two actions of this skill).\\

	\hfill
	\begin{tabular}{rr}
		Costs: & 500 \\
		Res: & 13 \\
	\end{tabular}
\end{skill}

